---
title: "Statistics 6371 Final Project"
author: "Sean Kennedy"
date: "August 7, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sqldf)
```

## prime data sources

```{r}
housing_train = read.csv('../data/train.csv')
housing_test = read.csv('../data/test.csv')

```

## Century 21 Analysis 
  
   Only analyze neighborhoods NAmes, Edwards, BrkSide
   
   Answer:
    
   Does SalePrice depend on GrLivArea?
   
   Does the effect vary by neighborhood?
   
  
##  Build and Fit the Model
	 
	- Checking Assumptions 
		
		Test for outliers (from SAS):
		
		
		Residual Plots 
		Influential point analysis (Cook's D and Leverage)
		Make sure to address each assumption.

	Comparing Competing Models
		Adj R2  
		Internal CV Press  
	
	Parameters
		Estimates
		Interpretation 
		Confidence Intervals 

Conclusion
	A short summary of the analysis.

   
```{r}

neighborhood_data = sqldf("SELECT 
                            Id  
                            , Neighborhood
                            , GrLIvArea
                            , SalePrice
                          FROM 
                          housing_train 
                          WHERE 
                          Neighborhood IN ('NAmes','Edwards', 'BrkSide')")

summary(neighborhood_data)
```

## Strategy
    Create a simple regression model where we encode neighborhood as a categroical variable and see if 
    intercepts/coefficients vary amongst neighborhoods
    

## Check Assumptions of Linear Regression Model
